---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# agstudy1app -- GPACH Surveillance of Agriculture Injuries in Iowa Web Application Package

The goal of agstudy1app is to be a supplementary package for the GPCAH Surveillance of Agriculture Injuries in Iowa Web Application.

## Installation

You can install the development version of agstudy1app from [GitHub](https://github.com/deboonstra/agstudy1app/tree/main) with:

## Installation
```r
# install.packages("remotes")
remotes::install_github("deboonstra/agstudy1app")
```

## Useage

This is a basic example which shows you how to calculate the predicted probabilities of a forty-five year old injured person using the `pred_prob` function.

```{r, eval = FALSE}
library(agstudy1app)
agstudy1app::pred_prob(age = mean(agstudy1app::iwc_itr_only$age))
```
```{r, eval = TRUE, echo = FALSE}
library(agstudy1app)
library(knitr)
tab <- agstudy1app::pred_prob(age = mean(agstudy1app::iwc_itr_only$age))
knitr::kable(x = tab, format = "pipe")
```

### Parameter values
The possible valid injury characteristics are listed in the help document for `pred_prob`.
```{r, eval = FALSE}
?agstudy1app::pred_prob()
```