---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# agstudy1app -- GPACH Surveillance of Agriculture Injuries in Iowa Web Application Package

The goal of `agstudy1app` is to be a supplementary package for the GPCAH Surveillance of Agriculture Injuries in Iowa Web Application, https://ph-ivshiny.iowa.uiowa.edu/deboonstra/agstudy1app/.

## Installation

You can install the development version of `agstudy1app` package from [GitHub](https://github.com/deboonstra/agstudy1app/tree/main) with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("deboonstra/agstudy1app")
```

## Useage

This is a basic example which shows you how to calculate the predicted probabilities of a forty-five year old injured person using the `pred_prob` function.

```{r, eval = FALSE}
library(agstudy1app)
agstudy1app::pred_prob(age = 45)
```
```{r, eval = TRUE, echo = FALSE}
library(agstudy1app)
library(knitr)
tab <- agstudy1app::pred_prob(age = 45)
knitr::kable(x = tab, format = "pipe")
```

### Parameter values
The possible valid injury characteristics are listed in the help document for `pred_prob`.
```{r, eval = FALSE}
?agstudy1app::pred_prob()
```

## On-device useage of web application

Currently, the web application does not allow the user to download the predicted probabilities calculated. Therefore, to obtain the probabilities for external use, installation of the [`agstudy1app`](https://github.com/deboonstra/agstudy1app) package is required. Then, simply call the `agstudy1app::pred_prob()` function with the injury characteristics of interest. If one choose to run the web application on their local machine, they will need to `git clone` the [`agstudy1app`](https://github.com/deboonstra/agstudy1app) repository to their desired location. Then, in an interactive session of *R*, where `agstudy1app` is the current working directory, execute the following command.

```{r, eval = FALSE}
agstudy1app::app()
```